Achieving maximum possible precision on stellar radial-velocity measurements in multi-epoch spectroscopy

### 2017-12-11 paper/paper.tex
first shot at acks

...paragraph for each major result from the abstract

@@

\acknowledgements
MPIA hospitality, Montet, Foreman-Mackey, Bean, Stuermer, Rix, \HARPS\ team, ESO, Stars group meeting, Brewer

>>>>

...insert here one paragraph for each major result from the
abstract. Each paragraph should emphasize the awesome of the result,
but then discuss limitations or interpretation...

@@

\acknowledgements
It is a pleasure to thank
  Jacob Bean (Chicago),
  John Brewer (Yale),
  Dan Foreman-Mackey (Flatiron),
  Ben Montet (Chicago),
  Hans-Walter Rix (MPIA),
  Julian Stuermer (Chicago),
and the participants in the weekly Stars Group Meeting at the Flatiron
Institute for valuable contributions to this project.
None of this would have been possible without the incredible effort
of the \HARPS\ team and \ESO, who built the instrument and made the
data used here public.
MB thanks the Max-Planck-Institut f\"ur Astronomie in Heidelberg
for hospitality during a critical phase of this project.

\todo{add Hogg grant numbers}
